\thetitle

### 2020-11-18 sun_phases/spin_qudit_tomo.tex
enforce trace-1 for the state maximizing reconstruction error

Consider a $d$-state spin qudit with total spin $s\equiv\frac{d-1}{2}$.
The defining property of a spin qudit is the fact that it describes an angular momentum degree of freedom, which has specific implications for how a spin qudit should transform under the group SO(3) of rotations in 3D space.
Due to the central importance of these transformation rules for a spin qudit, we first identify a basis of operators that transforms nicely under 3D rotations.
One such basis is provided by the {\it transition operators} (also known as polarization operators \cite{kryszewski2006positivity, bertlmann2008bloch}), defined by
\begin{align}
  T_{\ell m} \equiv \sqrt{\f{2\ell+1}{2s+1}} \sum_{\mu,\nu=-s}^s
  \bk{s\mu;\ell m|s\nu} \op{\nu}{\mu},
  \label{eq:trans_op}
\end{align}
where $\bk{s\mu;\ell m|s\nu}$ is a Clebsh-Gordan coefficient that enforces $\ell\in\set{0,1,\cdots,d-1}$ and $m\in\set{-\ell,-\ell+1,\cdots,\ell}$, such that there are $d^2$ operators in total.
For brevity, we will generally treat the value of $d$ (or $s$) as constant but arbitrary throughout this work, and suppress any explicit dependence of quantities or operators such as $T_{\ell m}$ on $d$.
The transition operators are orthonormal with respect to the trace inner product, and transform nicely under conjugation:
\begin{align}
  \obk{T_{\ell m }|T_{\ell'm'}}
  = \delta_{\ell\ell'} \delta_{mm'},
  &&
  T_{\ell m}^\dag = \p{-1}^m T_{\ell,-m},
\end{align}
where for any $d\times d$ matrix $X=\sum_{\mu,\nu} X_{\mu\nu} \op{\mu}{\nu}$ we define the $d^2$-component vector $\oket{X} \equiv \sum_{\mu,\nu} X_{\mu\nu} \ket{\mu\nu}$; $\obra{X}$ is the conjugate transpose of $\oket{X}$, such that $\obk{X|Y}=\tr\p{X^\dag Y}$; and $\delta_{kk'}\equiv 1$ if $k=k'$ and $0$ otherwise.
These properties of the transition operators allow us to expand any density operator $\rho$ in the transition operator basis as
\begin{align}
  \rho = \sum_{\ell=0}^{d-1} \sum_{m=-\ell}^\ell
  \rho_{\ell m} T_{\ell m},
  &&
  \rho_{\ell m} \equiv \bk{T_{\ell m}^\dag}_\rho,
  \label{eq:trans_state}
\end{align}
where $\bk{X}_\rho\equiv\tr\p{\rho X}$, and $\rho^\dag=\rho$ implies that $\rho_{\ell m}^*=\p{-1}^m\rho_{\ell,-m}$.
The transition operators can be physically interpreted as the transition $\ket\psi\to T_{\ell m}\ket\psi$ induced on the state $\ket\psi$ of a spin-$s$ system by the absorption of a spin-$\ell$ particle with spin projection $m$ onto a fixed quantization axis.
In analogy with the spherical harmonics $Y_{\ell m}$, we will refer to the index $\ell$ as the {\it degree} and $m$ as the {\it order} of $T_{\ell m}$.

@@

Reconstructing an arbitrary density operator $\rho$ essentially requires us to find a set of axes $V=\set{\v v}$ and associated coefficients $C_{\ell mk}\p{\v v}$ that would allow us to recover any coefficient $\rho_{\ell m}$ in the expansion in Eq.~\eqref{eq:trans_state} through
\begin{align}
  \rho_{\ell m} = \bk{T_{\ell m}^\dag}_\rho
  = \sum_{\v v,k} C_{\ell mk}\p{\v v} \bk{T_{\v vk,0}^\dag}_\rho.
  \label{eq:state_recon}
\end{align}
Expanding the rotated transition operators $T_{\v vk,0}$ into a sum of un-rotated transition operators, according to Eq.~\eqref{eq:trans_rot}, we find that the recovery condition in Eq.~\eqref{eq:state_recon} is satisfied when
\begin{align}
  T_{\ell m}^\dag
  = \sum_{\v v,k,n} C_{\ell mk}\p{\v v}
  D^k_{n,0}\p{\v v}^* T_{kn}^\dag.
\end{align}
Orthogonality of the transition operators motivates the ansatz $C_{\ell mk}\p{\v v}=\delta_{k\ell}C_{\ell m}\p{\v v}$, which in turn implies that
\begin{align}
  \sum_{\v v} C_{\ell m}\p{\v v} D^\ell_{n,0}\p{\v v}^* = \delta_{mn}
  \label{eq:tomo_recovery}
\end{align}
for all $\ell$.

In fact, the problem of finding suitable axes $V$ and coefficients $C_{\ell m}\p{\v v}$ to satisfy Eq.~\eqref{eq:tomo_recovery}, solving which would enable the recovery of arbitrary spin qudit states, can be mapped onto the well-studied problem of signal recovery on the sphere \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality}.
The signal recovery problem can be stated as follows: given a square-integrable function $f$ on the sphere, with the harmonic expansion
\begin{align}
  f\p{\v v} = \sum_{\ell,m} f_{\ell m} Y_{\ell m}\p{\v v},
\end{align}
where $f_{\ell m}$ are expansion coefficients and $Y_{\ell m}$ is the spherical harmonic of degree $\ell$ and order $m$, find a set of points $V=\set{\v v}$ and associated coefficients $\tilde C_{\ell m}\p{\v v}$ with which we can reconstruct $f$, or equivalently its coefficients $f_{\ell m}$, from knowledge of the function's value $f\p{\v v}$ at all points $\v v\in V$; that is
\begin{align}
  f_{\ell m} = \sum_{\v v} \tilde C_{\ell m}\p{\v v} f\p{\v v}
  = \sum_{\v v,k,n} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v} f_{kn}.
\end{align}
Reconstruction of functions with arbitrary coefficients $f_{\ell m}$ implies that
\begin{align}
  \sum_{\v v} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v}
  = \delta_{k\ell} \delta_{mn},
  \label{eq:full_recovery}
\end{align}
which is a stronger version of the condition that we found for the spin qudit tomography problem in Eq.~\eqref{eq:tomo_recovery}.
We will refer to Eq.~\eqref{eq:full_recovery} as the {\it full recovery problem}, and Eq.~\eqref{eq:tomo_recovery} as the the {\it reduced recovery problem}.
Due to the fact that $D^k_{n,0}\p{\v v}^* = \sqrt{\frac{4\pi}{2\ell+1}}\, Y_{kn}\p{\v v}$, any solution to the full recovery problem automatically solves the reduced recovery problem by setting $C_{\ell m}\p{\v v} = \sqrt{\frac{2\ell+1}{4\pi}}\, \tilde C_{\ell m}\p{\v v}$.
In principle, this mapping allows us to import a host of existing signal recovery algorithms \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality} for the task of spin qudit tomography.
In practice, spin qudits typically have only a modest dimension $d$, which allows for simpler and optimized tomography protocols that are practical despite worse scaling with $d$ (see Section \ref{sec:protocol}).

@@

where $\norm{X} \equiv \sqrt{\obk{X|X}} = \sqrt{\tr\p{X^\dag X}}$ is the (Hilbert-Schmidt, or Frobenius) norm of $X$, and the {\it classical error scale}

@@

The assumption that observables can be estimated up to uncorrelated noise with maximal variance $\epsilon^2$, summarized by Eq.~\eqref{eq:error_assumption}, is reasonable when measurement error is dominated by classical sources of experimental noise.
However, this assumption breaks down when measurement error is limited by fundamental quantum (shot) noise.
We relax the assumption of Eq.~\eqref{eq:error_assumption} in Appendix \ref{sec:error}, where we instead assume that $\tilde\rho_V$ is built from $n$ independent measurements of spin projection along every axis $\v v\in V$, with shot noise the dominant source of error.
In this case, the mean squared distance between the approximation $\tilde\rho_V$ and the true state $\rho$ can be compactly expressed using trace inner products of the {\it covariance matrices}
\begin{align}
  \C_\ell\sp{\rho} \equiv \sum_{m,n=-\ell}^\ell
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n}
\end{align}
where $\cov_\rho\p{X,Y} \equiv \bk{XY}_\rho - \bk{X}_\rho \bk{Y}_\rho$, and the {\it noise matrices}
\begin{align}
  \N_{V\ell} \equiv M_{V\ell} \diag\sp{M_{V\ell}^{-1}
    \p{M_{V\ell}^{-1}}^\dag} M_{V\ell}^\dag,
\end{align}
where $\diag\sp{X}$ sets all off-diagonal parts of $X$ to zero:
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \obk{\N_{V\ell}|\C_\ell\sp{\rho}}.
  \label{eq:error}
\end{align}
Maximizing this error over all $\rho$ (for a fixed set of axes $V$) yields a reconstruction error bound of the form
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2} \le \f{\epsilon_V^2}{n},
  \label{eq:bound}
\end{align}
where the complexity of computing the {\it quantum error scale} $\epsilon_V^2$ (defined below) is the same as that of computing the classical error scale $\S_V^2$ (see Figure \ref{fig:times}).
For comparison with the bound in Eq.~\eqref{eq:bound_eps}, we note that $\epsilon_V^2<\S_V^2/2$, so the previous bound still holds with the replacement $\epsilon^2\to1/2n$.
We also note that the (squared) reconstruction error in Eq.~\eqref{eq:error} and its bound in Eq.~\eqref{eq:bound} obey the ``standard quantum limit'' of $\sim1/\sqrt{n}$ scaling in the number of measurements.
In principle, this scaling can be improved to $\sim1/n$ by preparing and measuring entangled copies of many qudits \cite{giovannetti2006quantum}.

@@

The remainder of this section is devoted to defining the quantum error scale $\epsilon_V^2$ (derived in Appendix \ref{sec:error}), and can be skipped without consequence for the discussions in the rest of this paper.
To write out $\epsilon_V^2$ explicitly, we define a matrix of structure constants
\begin{align}
  g_{L\ell} \equiv \sum_{m,n=-\ell}^\ell
  \obk{T_{L,m+n}|T_{\ell m}T_{\ell n}} \op{m}{n},
\end{align}
and the inversion operator $\I\equiv\sum_m\p{-1}^m\op{-m}{m}$, which are used to define the $\p{2\ell+1}$-component vectors
\begin{align}
  \ket{\chi_{V\ell}}
  &\equiv \sum_{m=-\ell}^\ell \chi^V_{\ell m} \ket{m}, \\
  \chi^V_{LM} &\equiv \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on, such that $\obk{\N_{V\ell}|\D_M|\I g_{L\ell}}$ is an inner product between the $M$-th diagonals of $\N_{V\ell}$ and $\I g_{L\ell}$.
The vectors $\ket{\chi_{V\ell}}$ allow us to express reconstruction error in the simple form
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \sp{\bk{\chi_{V\ell}|\rho_\ell}
    - \bk{\rho_\ell|\N_{V\ell}|\rho_\ell}},
\end{align}
where $\ket{\rho_\ell}\equiv\sum_m \rho_{\ell m}\ket{m}$.
This error is straightforward to maximize with respect to all states $\rho$, which yields the bound in Eq.~\eqref{eq:bound} with $\epsilon_V^2 \equiv \sum_\ell \epsilon_{V\ell}^2$ and
\begin{align}
  \epsilon_{V\ell}^2 \equiv
  \bk{\chi_{V\ell}|\p{\L_{V\ell}^{-1}
      - \L_{V\ell}^{-1}\N_{V\ell}\L_{V\ell}^{-1}}|\chi_{V\ell}},
\end{align}
where
\begin{align}
  \L_{V\ell} \equiv \N_{V\ell} + \I\N_{V\ell}\I.
\end{align}

@@

  D^\ell_{m,0}\p{\v v_i}^* D^\ell_{m',0}\p{\v v_i}

@@

  = \f1n \sum_\ell \obk{\N_{V\ell}|\C_\ell\sp{\rho}}.

@@

@@

  \rho_{\ell m'} \rho_{\ell m},

@@

In total, reconstruction error can be written in the form
  = \obk{\chi_V|\rho}
  - \sum_\ell \obk{\rho|U_\ell\N_{V\ell}U_\ell^\dag|\rho},
  \oket{\chi_V} \equiv \sum_{L,M} \chi^V_{LM} \oket{T_{LM}},
  U_\ell \equiv \sum_m \oket{T_{\ell m}} \bra{m}.
Performing the change of basis $\oket{T_{\ell m}}\to\ket{\ell m}$ by defining
  \ket{\rho} \equiv U^\dag \oket{\rho}
  = \sum_{\ell,m} \rho_{\ell m}\ket{\ell m},
  \ket{\chi_V} \equiv U^\dag \oket{\chi_V}
  = \sum_{\ell,m} \chi^V_{\ell m} \ket{\ell m},
as well as the degree-$\ell$ projections

@@

  \ket{\chi_{V\ell}} \equiv \sum_m \chi^V_{\ell m} \ket{m},

@@

we can more simply write

@@

Given the expansion in Eq.~\eqref{eq:error_comps}, this error is straightforward to maximize by considering its variation with respect to $\rho_{\ell m}$:

@@

  - \sum_{m'} \sp{\bk{m'|\I\N_{V\ell}|m} + \bk{m'|\I\N_{V\ell}|m}}

@@

  \ket{\chi_{V\ell}} - \L_{V\ell} \ket{\rho_{V\ell}^\star} = 0,

@@

  \ket{\rho_{V\ell}^\star} = \L_{V\ell}^{-1} \ket{\chi_{V\ell}},

@@

and in turn

@@

  = \f{\epsilon_V^2}{n},

@@

  \epsilon_V^2 \equiv \sum_\ell \epsilon_{V\ell}^2,
  \epsilon_{V\ell}^2 \equiv \bk{\chi_{V\ell}|\p{\L_{V\ell}^{-1}
      - \L_{V\ell}^{-1}\N_{V\ell}\L_{V\ell}^{-1}}|\chi_{V\ell}}.
Note that the bound in Eq.~\eqref{eq:bound_SM} is obtained by maximizing reconstruction error over all possible $\rho$ regardless of their spectrum, which implies that the maximizer $\rho_V^\star$ may generally be an unphysical state with negative eigenvalues.

>>>>

Consider a $d$-state spin qudit with total spin $s\equiv\frac{d-1}{2}$.
The defining property of a spin qudit is the fact that it describes an angular momentum degree of freedom, which has specific implications for how a spin qudit should transform under the group SO(3) of rotations in 3D space.
Due to the central importance of these transformation rules for a spin qudit, we first identify a basis of operators that transforms nicely under 3D rotations.
One such basis is provided by the {\it transition operators} (also known as polarization operators \cite{kryszewski2006positivity, bertlmann2008bloch}), defined by
\begin{align}
  T_{\ell m} \equiv \sqrt{\f{2\ell+1}{2s+1}} \sum_{\mu,\nu=-s}^s
  \bk{s\mu;\ell m|s\nu} \op{\nu}{\mu},
  \label{eq:trans_op}
\end{align}
where $\bk{s\mu;\ell m|s\nu}$ is a Clebsh-Gordan coefficient that enforces $\ell\in\set{0,1,\cdots,d-1}$ and $m\in\set{-\ell,-\ell+1,\cdots,\ell}$, such that there are $d^2$ operators in total.
For brevity, we will generally treat the value of $d$ (or $s$) as constant but arbitrary throughout this work, and suppress any explicit dependence of quantities or operators such as $T_{\ell m}$ on $d$.
The transition operators are orthonormal with respect to the trace inner product, and transform nicely under conjugation:
\begin{align}
  \obk{T_{\ell m }|T_{\ell'm'}}
  = \delta_{\ell\ell'} \delta_{mm'},
  &&
  T_{\ell m}^\dag = \p{-1}^m T_{\ell,-m},
\end{align}
where for any $d\times d$ matrix $X=\sum_{\mu,\nu} X_{\mu\nu} \op{\mu}{\nu}$ we define the $d^2$-component vector $\oket{X} \equiv \sum_{\mu,\nu} X_{\mu\nu} \ket{\mu\nu}$; $\obra{X}$ is the conjugate transpose of $\oket{X}$, such that $\obk{X|Y}=\tr\p{X^\dag Y}$; and $\delta_{kk'}\equiv 1$ if $k=k'$ and $0$ otherwise.
These properties of the transition operators allow us to expand any density operator $\rho$ in the transition operator basis as
\begin{align}
  \rho = \sum_{\ell=0}^{d-1} \sum_{m=-\ell}^\ell
  \rho_{\ell m} T_{\ell m},
  &&
  \rho_{\ell m} \equiv \bk{T_{\ell m}^\dag}_\rho,
  \label{eq:trans_state}
\end{align}
where $\bk{X}_\rho\equiv\tr\p{\rho X}=\obk{\rho|X}$, and $\rho^\dag=\rho$ implies that $\rho_{\ell m}^*=\p{-1}^m\rho_{\ell,-m}$.
The transition operators can be physically interpreted as the transition $\ket\psi\to T_{\ell m}\ket\psi$ induced on the state $\ket\psi$ of a spin-$s$ system by the absorption of a spin-$\ell$ particle with spin projection $m$ onto a fixed quantization axis.
In analogy with the spherical harmonics $Y_{\ell m}$, we will refer to the index $\ell$ as the {\it degree} and $m$ as the {\it order} of $T_{\ell m}$.

@@

Reconstructing an arbitrary density operator $\rho$ essentially requires us to find a set of axes $V=\set{\v v}$ and associated coefficients $C_{\ell mk}\p{\v v}$ that would allow us to recover any coefficient $\rho_{\ell m}$ in the expansion in Eq.~\eqref{eq:trans_state} through
\begin{align}
  \rho_{\ell m}^* = \bk{T_{\ell m}}_\rho
  = \sum_{\v v,k} C_{\ell mk}\p{\v v} \bk{T_{\v vk,0}}_\rho.
  \label{eq:state_recon}
\end{align}
Expanding the rotated transition operators $T_{\v vk,0}$ into a sum of un-rotated transition operators, according to Eq.~\eqref{eq:trans_rot}, we find that the recovery condition in Eq.~\eqref{eq:state_recon} is satisfied when
\begin{align}
  T_{\ell m}
  = \sum_{\v v,k,n} C_{\ell mk}\p{\v v}
  D^k_{n,0}\p{\v v} T_{kn}.
\end{align}
Orthogonality of the transition operators motivates the ansatz $C_{\ell mk}\p{\v v}=\delta_{k\ell}C_{\ell m}\p{\v v}$, which in turn implies that
\begin{align}
  \sum_{\v v} C_{\ell m}\p{\v v} D^\ell_{n,0}\p{\v v} = \delta_{mn}
  \label{eq:tomo_recovery}
\end{align}
for all $\ell$.

In fact, the problem of finding suitable axes $V$ and coefficients $C_{\ell m}\p{\v v}$ to satisfy Eq.~\eqref{eq:tomo_recovery}, solving which would enable the recovery of arbitrary spin qudit states, can be mapped onto the well-studied problem of signal recovery on the sphere \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality}.
The signal recovery problem can be stated as follows: given a square-integrable function $f$ on the sphere, with the harmonic expansion
\begin{align}
  f\p{\v v} = \sum_{\ell,m} f_{\ell m} Y_{\ell m}\p{\v v},
\end{align}
where $f_{\ell m}$ are expansion coefficients and $Y_{\ell m}$ is the spherical harmonic of degree $\ell$ and order $m$, find a set of points $V=\set{\v v}$ and associated coefficients $\tilde C_{\ell m}\p{\v v}$ with which we can reconstruct $f$, or equivalently its coefficients $f_{\ell m}$, from knowledge of the function's value $f\p{\v v}$ at all points $\v v\in V$; that is
\begin{align}
  f_{\ell m} = \sum_{\v v} \tilde C_{\ell m}\p{\v v} f\p{\v v}
  = \sum_{\v v,k,n} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v} f_{kn}.
\end{align}
Reconstruction of functions with arbitrary coefficients $f_{\ell m}$ implies that
\begin{align}
  \sum_{\v v} \tilde C_{\ell m}\p{\v v} Y_{kn}\p{\v v}
  = \delta_{k\ell} \delta_{mn},
  \label{eq:full_recovery}
\end{align}
which is a stronger version of the condition that we found for the spin qudit tomography problem in Eq.~\eqref{eq:tomo_recovery}.
We will refer to Eq.~\eqref{eq:full_recovery} as the {\it full recovery problem}, and Eq.~\eqref{eq:tomo_recovery} as the the {\it reduced recovery problem}.
Due to the fact that $D^k_{n,0}\p{\v v} = \sqrt{\frac{4\pi}{2\ell+1}}\, Y_{kn}\p{\v v}^*$, any solution to the full recovery problem automatically solves the reduced recovery problem by setting $C_{\ell m}\p{\v v} = \sqrt{\frac{2\ell+1}{4\pi}}\, \tilde C_{\ell m}\p{\v v}^*$.
In principle, this mapping allows us to import a host of existing signal recovery algorithms \cite{mcewen2011novel, rauhut2011sparse, alem2012sparse, khalid2014optimaldimensionality} for the task of spin qudit tomography.
In practice, spin qudits typically have only a modest dimension $d$, which allows for simpler and optimized tomography protocols that are practical despite worse scaling with $d$ (see Section \ref{sec:protocol}).

@@

where $\norm{X}^2 \equiv \obk{X|X} = \tr\p{X^\dag X}$ is the squared (Frobenius, or Hilbert-Schmidt) norm of $X$, and the {\it classical error scale}

@@

The assumption that observables can be estimated up to uncorrelated noise with maximal variance $\epsilon^2$, summarized by Eq.~\eqref{eq:error_assumption}, is reasonable when measurement error is dominated by classical sources of experimental noise.
However, this assumption breaks down when measurement error is limited by fundamental quantum (shot) noise.
We relax the assumption of Eq.~\eqref{eq:error_assumption} in Appendix \ref{sec:error}, where we instead assume that $\tilde\rho_V$ is built from $n$ independent measurements of spin projection along every axis $\v v\in V$, with shot noise the dominant source of error.
In this case, the mean squared distance between the approximation $\tilde\rho_V$ and the true state $\rho$ can be compactly expressed using trace inner products of the {\it covariance matrices}
\begin{align}
  \C_\ell\sp{\rho} \equiv \sum_{m,n=-\ell}^\ell
  \cov_\rho\p{T_{\ell m}^\dag, T_{\ell n}} \op{m}{n}
\end{align}
where $\cov_\rho\p{X,Y} \equiv \bk{XY}_\rho - \bk{X}_\rho \bk{Y}_\rho$, and the {\it noise matrices}
\begin{align}
  \N_{V\ell} \equiv M_{V\ell} \diag\sp{M_{V\ell}^{-1}
    \p{M_{V\ell}^{-1}}^\dag} M_{V\ell}^\dag,
\end{align}
where $\diag\sp{X}$ sets all off-diagonal parts of $X$ to zero:
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \obk{\N_{V\ell}|\C_\ell\sp{\rho}}.
  \label{eq:error}
\end{align}
Maximizing this error over all $\rho$ (for a fixed set of axes $V$) yields a reconstruction error bound of the form
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2} \le \f{\epsilon_V^2}{n},
  \label{eq:bound}
\end{align}
where the complexity of computing the {\it quantum error scale} $\epsilon_V^2$ (defined below) is the same as that of computing the classical error scale $\S_V^2$ (see Figure \ref{fig:times}).
For comparison with the bound in Eq.~\eqref{eq:bound_eps}, we note that $\epsilon_V^2<\S_V^2/2$, so the previous bound still holds with the replacement $\epsilon^2\to1/2n$.
We also note that the (squared) reconstruction error in Eq.~\eqref{eq:error} and its bound in Eq.~\eqref{eq:bound} obey the ``standard quantum limit'' of $\sim1/n$ scaling in the number of measurements.
In principle, this scaling can be improved to $\sim1/n^2$ by preparing and measuring entangled copies of many qudits \cite{giovannetti2006quantum}.

@@

The remainder of this section is devoted to defining the quantum error scale $\epsilon_V^2$ (derived in Appendix \ref{sec:error}), and can be skipped without consequence for the discussions in the rest of this paper.
To write out this error in full, we first rewrite the reconstruction error in Eq.~\eqref{eq:error} as
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \sp{\bk{\chi_{V\ell}|\rho_\ell}
    - \bk{\rho_\ell|\N_{V\ell}|\rho_\ell}},
  \label{eq:error_simp}
\end{align}
where $\ket{\rho_\ell}\equiv\sum_m \rho_{\ell m}\ket{m}$, and similarly $\ket{\chi_{V\ell}}\equiv\sum_m \chi^V_{\ell m} \ket{m}$ is a vector of the scalars $\chi^V_{\ell m}$ defined by
\begin{align}
  \chi^V_{LM} &\equiv
  \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  g_{L\ell} &\equiv \sum_{m,m'}
  \obk{T_{L,m+m'}|T_{\ell m}T_{\ell m'}} \op{m}{m'}, \\
  \I &\equiv \sum_m \p{-1}^m \op{-m}{m}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $g_{L\ell}$ is essentially a matrix of transition operator product coefficients (see Appendix \ref{sec:trans_prod}), and $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on.
Maximizing the reconstruction error in Eq.~\eqref{eq:error_simp} over all $\rho$ with $\tr\rho=1$ leads to the bound in Eq.~\eqref{eq:bound} with
\begin{align}
  \epsilon_V^2 \equiv \sum_\ell\sp{\bk{\chi_{V\ell}|\rho_{V\ell}^\star}
    - \bk{\rho_{V\ell}^\star|\N_{V\ell}|\rho_{V\ell}^\star}}
\end{align}
where the maximizers
\begin{align}
  \ket{\rho_{V\ell}^\star} \stackrel{\ell>0}{\equiv}
  \L_{V\ell}^{-1} \ket{\chi_{V\ell}},
  &&
  \ket{\rho_{V,0}^\star} \equiv \f1{\sqrt{d}} \ket{0},
\end{align}
are defined in terms of the inverse $\L_{V\ell}^{-1}$ of
\begin{align}
  \L_{V\ell} \equiv \N_{V\ell} + \I \N_{V\ell} \I.
\end{align}
Note that the bound in Eq.~\eqref{eq:bound} is obtained by maximizing the reconstruction error in Eq.~\eqref{eq:error_simp} over all possible $\rho$ (satisfying $\tr\rho=1$) regardless of their spectrum.
As a consequence, the maximizing ``state'' $\rho_V^\star$ may generally have negative eigenvalues.
In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound} by maximizing reconstruction error over the (restricted) domain of states with a non-negative spectrum.

@@

  D^\ell_{m',0}\p{\v v_i} \abs{\tilde{\v q}_{\ell i}}^2
  D^\ell_{m,0}\p{\v v_i}^*

@@

  = \f1n \sum_\ell \obk{\N_{V\ell}|\C_\ell\sp{\rho}},

@@

where $\obk{X|Y}=\tr\p{X^\dag Y}$ is a trace inner product.

@@

  \rho_{\ell m} \rho_{\ell m'},

@@

Defining the $\p{2\ell+1}$-component vectors

@@

  \ket{\chi_{V\ell}} \equiv \sum_{\ell,m} \chi^V_{\ell m} \ket{m},

@@

the expansion in Eq.~\eqref{eq:error_comps} is most efficiently evaluated in the vectorized form

@@

This error is straightforward to maximize by considering its variation with respect to $\rho_{\ell m}$:

@@

  - \sum_{m'} \sp{\bk{m'|\I\N_{V\ell}|m} + \bk{m|\I\N_{V\ell}|m'}}

@@

  \ket{\chi_{V\ell}} - \L_{V\ell} \ket{\rho_{V\ell}^\star}
  \stackrel{\ell>0}{=} 0,

@@

  \ket{\rho_{V\ell}^\star} \stackrel{\ell>0}{=}
  \L_{V\ell}^{-1} \ket{\chi_{V\ell}},
  \ket{\rho_{V,0}^\star} = \f1{\sqrt{d}} \ket{0},

@@

where the $\ell=0$ component of $\rho_V^\star$ enforces $\tr\rho_V^\star=1$.
We thus find that

@@

  = \f1n \sum_\ell \epsilon_{V\ell}^2,
  \epsilon_{V\ell}^2 \equiv \bk{\chi_{V\ell}|\rho_{V\ell}^\star}
  - \bk{\rho_{V\ell}^\star|\N_{V\ell}|\rho_{V\ell}^\star}.

@@

Note that the bound in Eq.~\eqref{eq:bound_SM} is obtained by maximizing reconstruction error over all possible $\rho$ (satisfying $\tr\rho=1$) regardless of their spectrum, which implies that the maximizer $\rho_V^\star$ may generally be an unphysical ``state'' with negative eigenvalues.
